### 2021-11-18 aifin/2021/project2/project2.tex
aifin project2

\lecture{Project 2: Paper Replication Study}{Yuan Yao}{Due: 23:59 Friday 12 Nov, 2021}{21 Oct, 2021}

@@

{\bf Deadline is \emph{11:59pm November 19, 2021}}. Submit your review in plain text to the email address (\url{aifin.hkust@gmail.com}) with title: \underline{MAFS6010Z: Project 2 Review}. Rebuttal is open afterwards.

@@

\section*{Rebuttal}
The rebuttal period starts from now, till \emph{11:59pm Nov 22, 2021}. Restrict the number of characters of your rebuttal within {\bf{5,000}}. Submit your rebuttal in PLAIN TEXT or PDF format to \textbf{canvas} with filename comprising the corresponding group number: e.g. \underline{rebuttal1\_group02.pdf}. %(\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 1 Rebuttal}.

>>>>

\lecture{Project 2: Paper Replication Study}{Yuan Yao}{Due: 23:59 Sunday 14 Nov, 2021}{21 Oct, 2021}

@@

{\bf Deadline is \emph{11:59pm November 21, 2021}}. Submit your review in plain text to the email address (\url{aifin.hkust@gmail.com}) with title: \underline{MAFS6010Z: Project 2 Review}. Rebuttal is open afterwards.

@@

\section*{Rebuttal}
The rebuttal period starts from now, till \emph{11:59pm Nov 24, 2021}. Restrict the number of characters of your rebuttal within {\bf{5,000}}. Submit your rebuttal in PLAIN TEXT or PDF format to \textbf{canvas} with filename comprising the corresponding group number: e.g. \underline{rebuttal1\_group02.pdf}. %(\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 1 Rebuttal}.
